### 2017-11-12 Draft2/Appendix.tex
Respond to feedback
Work

\appendix
\appendixpage

\section{Proving $\sim$ Properties}

\subsection{$\sim$ Merges over $+$, $\times$, and $\div$}
\label{pf:MergesOverArithmetic}
\begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
	% TODO: Prove statement for addition.

@@

\subsection{$\sim$ Removes Lower-Order Terms}
\label{pf:RemovesLowerOrderTerms}

\subsection{$\sim$ is Transitive}
\label{pf:Transitivity}

\begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
By definition, $\ExprNToInfty \dfrac f g = 1$ and $\ExprNToInfty \dfrac g h = 1$. Multiplying the two equations, $\ExprNToInfty \dfrac f h = 1$ which implies $f \sim h$.
\end{proof}

>>>>

% Todo: Name 'Appendix', not 'Appendices'
\appendix
\appendixpage

\section{Proofs of $\sim$ Properties}

\subsection{$\sim$ is an Equivalence Relation}

\begin{proof}[Proof (Theorem \ref{thm:EquivalenceRelation})]
	Clearly, $\ExprNToInfty \dfrac{f}{f} = 1$, so $f \sim f$. Thus, $\sim$ is reflexive.

	Suppose $f \sim g$. Then $\ExprNToInfty \dfrac{f}{g} = 1$. Since both $\ExprNToInfty 1$ and $\ExprNToInfty \dfrac{f}{g}$ exist and the latter is nonzero, $\dfrac{\ExprNToInfty 1}{\ExprNToInfty (f / g)}$ = $\ExprNToInfty \dfrac{g}{f}$. Since the left-hand side evaluates to $1$, $g \sim f$. Thus, $\sim$ is symmetric.

	Suppose $f \sim g$ and $g \sim h$. By definition, $\ExprNToInfty \dfrac{f}{g} = 1$ and $\ExprNToInfty \dfrac{g}{h} = 1$. Since both limits exist, their product is $\ExprNToInfty \left( \dfrac{f}{g} \cdot \dfrac{g}{h} \right) = \ExprNToInfty \dfrac{f}{h}$. Since this product is $1$, $f \sim h$. Thus, $\sim$ is transitive.
\end{proof}

\subsection{$\sim$ Removes Lower-Order Terms}

\subsection{$\sim$ Merges over $+$, $\times$, and $\div$}

\begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
	% TODO: Prove statement for addition.

@@

### 2017-11-12 Draft2/AsymptoticNotation.tex
Work

The following theorem states that $\sim$ can ``merge,'' or un-distribute, over addition, multiplication, and division. This is a property shared with big-O.

\begin{theorem}
\label{thm:MergesOverOps}
	Suppose $f$, $\Tweak{f}$, $g$, and $\Tweak{g}$ are functions. If $f \sim \Tweak{f}$ and $g \sim \Tweak{g}$, then
	\begin{align*}
	f + g &\sim \Tweak{f} + \Tweak{g}\\
	fg &\sim \Tweak{f}\Tweak{g}\\
	\frac{f}{g} &\sim \frac {\Tweak{f}} {\Tweak{g}}
	\end{align*}
\end{theorem}

The following theorem states that lower-order terms may be removed: for example, $(n + \log_2 n) \sim n$. This is also a property shared with big-O.

@@

The following theorem states that $\sim$ is a transitive relation. This property is used implicitly by proofs that chain multiple $\sim$ signs in the form $f \sim g \sim h$, and then conclude that $f \sim h$.

\begin{theorem}
\label{thm:SimIsTransitive}
	If $f \sim g$ and $g \sim h$, then $f \sim h$.
\end{theorem}

@@

>>>>

In the following theorems, variables with the letters $f$, $g$, or $h$ denote arbitrary, non-decreasing functions with positive outputs for sufficiently large $n$.

The following theorem states that $\sim$ meets the requirements of an equivalence relation.

\begin{theorem}
\label{thm:EquivalenceRelation}
	$\sim$ is reflexive, transitive, and symmetric.
\end{theorem}

The following theorem states that lower-order terms may be removed: for example, $(n + \log_2 n) \sim n$. This is a property shared with big-O.

@@

\begin{corollary}
\label{coro:PlusConstant}
	If $f$ is unbounded, then $f + c \sim f$ for any constant $c$.
\end{corollary}

The following theorem states that $\sim$ can ``merge,'' or un-distribute, over addition, multiplication, and division. This is also a property shared with big-O.

\begin{theorem}
\label{thm:MergesOverOps}
	If $f \sim \Tweak{f}$ and $g \sim \Tweak{g}$, then
	\begin{align*}
	f + g &\sim \Tweak{f} + \Tweak{g}\\
	fg &\sim \Tweak{f}\Tweak{g}\\
	\frac{f}{g} &\sim \frac {\Tweak{f}} {\Tweak{g}}
	\end{align*}
\end{theorem}

\begin{corollary}
	Both sides of a $\sim$ relation may be added, multiplied, or divided by the same function.
\end{corollary}

@@

\begin{corollary}
	The same statements hold true for $\FluteLeq$: If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLeq \TweakSecond{f}$, then $f \FluteLeq \TweakSecond{f}$. If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLeq \TweakSecond{g}$, then $\Tweak{g} \FluteLeq g$.
\end{corollary}

\begin{corollary}
	Both sides of a $\FluteLess$ or $\FluteLeq$ relation may be added, multiplied, or divided by the same function.
\end{corollary}
